Automated data-driven symbolic modeling of the lift forces acting on flapping wings

### 2021-01-19 paper/main.tex
Edit Methods text

\section*{Methods}
Our experimental apparatus consisted of a wing and actuator mounted to a
vertical force sensor, with a high-speed video camera recording the motion of
the wing from a top-down view and (using a mirror) also from a side-view.
Figure~\ref{fig:apparatus} provides a diagram of the apparatus as well as
illustrations of the three primary variables describing the orientation of the
wing in the apparatus: Stroke ($\phi$), deflection ($\psi$) and deviation
($\theta$). The stroke motion is enabled by a hinge joint and is the only
actuated degree of freedom in the system. The deflection of the wing is enabled
by a hinge in the root of the wing, and is a passive motion resulting from both
inertial and aerodynamic effects. Deviation refers to the passive vertical
motion of the wing out of its horizontal flapping plane, and is enabled only by
the tolerances of the hinges and the flexibility of the wing structure itself.

>>>>

\section*{Methods}
Our experimental apparatus consisted of a wing and actuator mounted to a
vertical force sensor, with a high-speed video camera recording the motion of
the wing from a top-down view and (using a mirror) also from a side-view. The
top-down and side views were used to detect and track the orientation of the
wing.  Figure~\ref{fig:apparatus} provides a diagram of the apparatus as well as
illustrations of the three primary variables describing the wing orientation:
Stroke ($\phi$), deflection ($\psi$) and deviation ($\theta$). The stroke motion
is enabled by a hinge joint and is the only actuated degree of freedom in the
system. The deflection of the wing is enabled by a hinge in the root of the
wing, and is a passive motion resulting from both inertial and aerodynamic
effects. Deviation refers to the passive vertical motion of the wing out of its
horizontal flapping plane, and is enabled only by the tolerances of the hinges
and the flexibility of the wing structure itself. These three variables, and
their derivatives, are some of the inputs required to model lift forces. The
other inputs are the geometric and inertial properties of the wings, obtained
from CAD designs and physical measurement. Next, we describe the wing design and
fabrication, the force measurement apparatus, and the method of extracting wing
kinematics from high-speed video.
